---
title: "Lab 01 - Hello R"
author: "Yiwei Tang"
date: "1/15/2026"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

There are 1846 rows and 3 columns in datasaurus_dozen. The three variables are dataset, x, and y.

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

It is important to visualize the data before analyzing it statistically. In this case, we can see clearly that the graph is non-linear; therefore, it doesn't make sense to test the correlation between the x and y.

### Exercise 3

Here, I plotted the star dataset and calculated the correlation coefficient between x and y in star.

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
Similar to the dino dataset, the x and y of star are used to plot a representation of a object, a star. Therefore, the correlation coefficient here is not meaningful.

### Exercise 4

Here, I plotted the dataset circle and calculated the correlation coefficient between x and y in circle.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


